---
title: "Sparks_Foundation_Task1_ScoresHours_Devanshi_Varshney"
author: "Devanshi Varshney "
date: "10/05/2021"
output: pdf_document
---

# Task 1 Data Science and Business Analytics Internship

```{r warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
```

```{r}
df<-read.csv("C:/Users/devan/Downloads/student_scores.csv")

head(df)
```


## Analysing the dataset
the range of the columns, mean, median, missing values will give an
insight of the dataset I will work upon.
```{r}
#insight
summary(df)

#structure
str(df)

#check for missing values
colSums(is.na(df))
```

## Creating a linear regression model
the model will show the relation between the marks scored by a 
student and the number of hours of study he/she had put in daily.

```{r}
model<-lm(Scores~Hours, data=df)
model

```
## Visualizing the Line od Regression
to see how our data is distributed around the regression line.
```{r}
ggplot(df, aes(Hours, Scores))+geom_point()+stat_smooth(method = lm)+theme_light()
```


## Answer of the question in the task
we will use the above created model to form the linear equation
by using the intercept and slope of the model.
Then replace hours with 9.25 as per the question to get the answer.
```{r}
model$coefficients

hrs<-9.25
scr<-2.484+(9.776*hrs)
scr
```

Result:
If a student studies for 9.25 hours, he/she will score approximately 92.912 ~ 93 marks

